An Improved ANS Transaction Template

### 2018-01-26 paper.tex
adding a table

The second step determines how to populate the cascade with the user-defined maximum number of centrifuges. One first solves the linear flow equation to determine the theoretical flow in the
cascade:
\begin{strip}
\begin{equation}
\setcounter{MaxMatrixCols}{20}
\begin{bmatrix}
-1         & 1-\theta_{S+1} & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
\theta_{S} & -1             & 1-\theta_{S+2} & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
           &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
0          & 0              & 0              & 0 & ... & 0 & \theta_{-1}  & -1  & 1 - \theta_{1} & 0 & ... & 0            & 0            & 0 \\
           &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & \theta_{E-2} & -1           & 1-\theta_{E} \\
0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & \theta_{E-1} & -1
\end{bmatrix}
\times
\begin{bmatrix}
     F_{S}   \\
     F_{S+1} \\
     \cdots  \\
     F_{0}   \\
    \cdots   \\
    F_{E-1}  \\
    F_{E}
\end{bmatrix}
=
\begin{bmatrix}
     0   \\
     0 \\
     \cdots  \\
     F   \\
    \cdots   \\
    0  \\
    0
\end{bmatrix}
\caption{caption needed!}
\label{eq:flow}
\end{equation}
\end{strip}
Once the relative flow of each stage, $F_{i}$, has been determined, the
cascade can be populated with actual machines up the stages
until either the maximum number available of machines or the maximum feed
flow is reached.

@@

\begin{table}[htb]
\centering
\begin{tabular}{lllll}
\toprule

@@

>>>>

The second step determines how to populate the cascade with the user-defined maximum number of centrifuges. One first solves the linear flow equation to determine the theoretical flow in the
cascade:
\begin{strip}
\begin{equation}
\setcounter{MaxMatrixCols}{20}
\begin{bmatrix}
-1         & 1-\theta_{S+1} & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
\theta_{S} & -1             & 1-\theta_{S+2} & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
           &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
0          & 0              & 0              & 0 & ... & 0 & \theta_{-1}  & -1  & 1 - \theta_{1} & 0 & ... & 0            & 0            & 0 \\
           &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & \theta_{E-2} & -1           & 1-\theta_{E} \\
0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & \theta_{E-1} & -1
\end{bmatrix}
\times
\begin{bmatrix}
     F_{S}   \\
     F_{S+1} \\
     \cdots  \\
     F_{0}   \\
    \cdots   \\
    F_{E-1}  \\
    F_{E}
\end{bmatrix}
=
\begin{bmatrix}
     0   \\
     0 \\
     \cdots  \\
     F   \\
    \cdots   \\
    0  \\
    0
\end{bmatrix}
%\caption{caption needed!}
\label{eq:flow}
\end{equation}
\end{strip}
Once the relative flow of each stage, $F_{i}$, has been determined, the
cascade can be populated with actual machines up the stages
until either the maximum number available of machines or the maximum feed
flow is reached.

@@

\begin{table}[htb]
\centering
\begin{tabular}{cllll}
\toprule

@@

\subsection{wWithout tail recycling}
Despite the reconfiguration of each level occuring in the second case, the case
1 is way more effective to produce HEU than case 1.
Indeed as observed on Figure \ref{} and \ref{}, the first case is able to
produce a an uranium product enrich at $98\%$ while the second case is only able
to reach an enrichment of $88.3\%$.
This is the consequence of the usage of un-touched cascade in the case 1:
because the cut value at each stage is unchanged it artificially produces over
enricht tails when feeded with higher enriched materials compared to a cascade
feed with the same feed assay but with a cascade designed for it.
The effective cut values for each cascade can be computed as :
\begin{equation}\label{eq:theta_eff}
    \theta = \dfrac{N - N''}{N'-N''}
\end{equation}

\begin{table}[htb]
\centering
\begin{tabular}{cll}
\toprule

Level   &  $\theta_{eff}^{C1}$   & $\theta_{eff}^{C2}$ \\ 
\midrule
1       & 0.109375               & 0.109375     \\
2       & 0.109375               & 0.128342     \\
3       & 0.109375               & 0.215694     \\
4       & 0.109375               & 0.411872     \\
5       & 0.109375               & 0.547009     \\

    Looks at the effective $\theta$ values of the cascade at the third level in both
case
